---
title: "PracticeProblems"
output: html_document
---

# Practice Problems

## Registering to Vote

### Freq

Use the data [here](https://raw.githubusercontent.com/chelseaparlett/CPSC540ParlettPelleriti/refs/heads/main/Data/23cw.csv) to analyze the relationship between various personal/demographic variables and **whether or not someone is registered to vote**. Fit a GLM appropriate for the question and use the output and ggplots to answer the questions below.

-   Is there a statistically significant relationship between **age** and whether someone is registered to vote?

-   Is there a statistically significant relationship between **income** and whether someone is registered to vote?

-   What is the best **interval estimate** for the effect of eating at Taco Bell on registering to vote?

-   How certain are we about the effect of being **White** on registering to vote? How can you tell?

-   Which state has the highest probability of being registered to vote?

```{r}
library(ggplot2)
```

### Bayes

Use `brms` to fit a similar Bayesian model with Weakly Informative (regularizing) priors on the coefficients (hint: `prior("normal(?,?)", class = "b")`). Are any of your inferences different from the frequentist model?

```{r}
library(brms)
```

## Spelling Scores

Use the data [here](https://raw.githubusercontent.com/chelseaparlett/CPSC540ParlettPelleriti/refs/heads/main/Data/23cw2.csv) to analyze the relationship between various personal/demographic variables and **schools standardized test scores**. Fit a Bayesian Mixed Effect GLM appropriate for the question and use the output and ggplots to answer the questions below.

-   How well do your **priors** fit what you expect about the data? (pp_check)

-   Is there evidence that **hair-color** has no effect on standardized test scores?

-   How much does the intercept for standardized test-scores **vary** between different school districts (used **random effects**)?

-   How much better are test scores per extra **100 calories a day**? Does this data provide evidence that it's beneficial for schools to hand out snacks to students leading up to the exam?

-   What is the probability that the regression coefficient for **`sleep`** is $\geq 5$ (meaning that an hour of extra sleep gives you a $+5$ predicted standardized test score)?

    ```{r}
    library(brms)
    library(bayesplot)
    library(tidybayes)

    ```
