---
title: "GLM Model Exercise"
output: html_document
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(brms)
library(ggplot2)
library(dplyr)
set.seed(540)
```

# Introduction to GLM Model Fitting

In this activity, you'll practice fitting various types of Generalized Linear Models (GLMs) using both frequentist approaches (`lm()`, `glm()`) and Bayesian approaches (`brms`).

## Worked Example: Simple Linear Regression

Let's start with a simple example to demonstrate both `lm()` and `brms()`

```{r example-data}
# Simple example: Height vs Weight
n <- 100
height_cm <- rnorm(n, mean = 170, sd = 10)
weight_kg <- 2.3 * height_cm - 320 + rnorm(n, mean = 0, sd = 8)
example_data <- data.frame(height_cm, weight_kg)

# Visualize
ggplot(example_data, aes(x = height_cm, y = weight_kg)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Height vs Weight", x = "Height (cm)", y = "Weight (kg)")
```

**Frequentist approach using lm():**

```{r example-lm}
# Fit linear model
model_lm <- lm(weight_kg ~ height_cm, data = example_data)
summary(model_lm)
```

**Bayesian approach using brms:**

```{r example-brms, results='hide'}
# Fit Bayesian linear model
model_brms <- brm(weight_kg ~ height_cm, 
                  data = example_data,
                  family = gaussian(),
                  chains = 2, 
                  iter = 2000,
                  refresh = 0)  # suppress output
```

```{r example-brms-summary}
summary(model_brms)
```

------------------------------------------------------------------------

## Data Generation

The code below generates your datasets for the next part of the activity.

```{r generate-data}
# Set seed for reproducibility
set.seed(540)

# Dataset 1: Student Test Scores (Linear Regression)
n1 <- 200
study_hours <- runif(n1, 0, 10)
test_score <- 65 + 3.2 * study_hours + rnorm(n1, 0, 8)
test_score <- pmax(0, pmin(100, test_score))  # bound between 0-100
dataset1 <- data.frame(
  study_hours = study_hours,
  test_score = test_score
)

# Dataset 2: Medical Treatment Success (Logistic Regression)
n2 <- 300
age <- rnorm(n2, 50, 15)
age <- pmax(18, pmin(85, age))
dosage_mg <- runif(n2, 10, 100)
logit_p <- -2 + 0.02 * age + 0.03 * dosage_mg
prob_success <- plogis(logit_p)
treatment_success <- rbinom(n2, 1, prob_success)
dataset2 <- data.frame(
  age = age,
  dosage_mg = dosage_mg,
  treatment_success = treatment_success
)

# Dataset 3: Exam Performance Proportion (Beta Regression)
n3 <- 150
prep_time <- runif(n3, 1, 20)
difficulty <- factor(sample(c("Easy", "Medium", "Hard"), n3, replace = TRUE))
difficulty_num <- as.numeric(difficulty)
mu_logit <- -1 + 0.15 * prep_time - 0.3 * difficulty_num
mu <- plogis(mu_logit)
# Simulate beta distribution
phi <- 15  # precision parameter
alpha <- mu * phi
beta <- (1 - mu) * phi
exam_proportion <- rbeta(n3, alpha, beta)
dataset3 <- data.frame(
  prep_time = prep_time,
  difficulty = difficulty,
  exam_proportion = exam_proportion
)

# Dataset 4: Hospital Admissions Count (Poisson Regression)
n4 <- 100
population_thousands <- runif(n4, 10, 200)
hospital_quality <- rnorm(n4, 0, 1)
lambda <- exp(1.5 + 0.01 * population_thousands + 0.2 * hospital_quality)
daily_admissions <- rpois(n4, lambda)
dataset4 <- data.frame(
  population_thousands = population_thousands,
  hospital_quality = hospital_quality,
  daily_admissions = daily_admissions
)

# Dataset 5: Customer Satisfaction (Ordered Logistic Regression)
n5 <- 400
service_rating <- rnorm(n5, 7, 2)
service_rating <- pmax(1, pmin(10, service_rating))
price_satisfaction <- rnorm(n5, 6, 1.5)
price_satisfaction <- pmax(1, pmin(10, price_satisfaction))

# Create ordered satisfaction levels
linear_pred <- -2 + 0.3 * service_rating + 0.4 * price_satisfaction
# Convert to ordered categories (1 = Very Unsatisfied, 5 = Very Satisfied)
# Create cumulative probabilities for 5 categories
thresholds <- c(-2, -1, 0, 1)
probs <- plogis(linear_pred)
satisfaction <- rep(1, n5)
for(i in 1:length(thresholds)) {
  satisfaction[linear_pred > thresholds[i]] <- i + 1
}
satisfaction <- pmin(satisfaction, 5)  # cap at 5

dataset5 <- data.frame(
  service_rating = service_rating,
  price_satisfaction = price_satisfaction,
  satisfaction = satisfaction
)

# Dataset 6: Website Click Counts (Negative Binomial Regression)
n6 <- 120
ad_spend_hundreds <- runif(n6, 1, 50)
website_age_years <- runif(n6, 0.5, 5)
mu <- exp(2 + 0.04 * ad_spend_hundreds - 0.15 * website_age_years)
daily_clicks <- rnbinom(n6, size = 5, mu = mu)  # overdispersed count data
dataset6 <- data.frame(
  ad_spend_hundreds = ad_spend_hundreds,
  website_age_years = website_age_years,
  daily_clicks = daily_clicks
)
```

------------------------------------------------------------------------

# Exercise 1: Student Test Scores

**Data:** This dataset contains information about students' study habits and test performance.

-   `study_hours`: Number of hours spent studying (0-10)
-   `test_score`: Final test score (0-100)

```{r explore-dataset1}
head(dataset1)
ggplot(dataset1, aes(x = study_hours, y = test_score)) +
  geom_point() +
  labs(title = "Study Hours vs Test Score")
```

**Question:** How does study time relate to test performance?

```{r exercise1-solution}
```

------------------------------------------------------------------------

# Exercise 2: Medical Treatment Success

**Data:** This dataset tracks medical treatment outcomes.

-   `age`: Patient age in years (18-85)
-   `dosage_mg`: Treatment dosage in milligrams (10-100)
-   `treatment_success`: Binary outcome (1 = success, 0 = failure)

```{r explore-dataset2}
head(dataset2)
ggplot(dataset2, aes(x = age, y = treatment_success)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "glm", method.args = list(family = "binomial")) +
  labs(title = "Age vs Treatment Success")
```

**Questions:** 1.
How do age and dosage affect treatment success probability?

```{r exercise2-solution}

```

------------------------------------------------------------------------

# Exercise 3: Exam Performance Proportions

**Data:** This dataset contains exam performance as proportions (0-1).

-   `prep_time`: Hours of preparation (1-20)
-   `difficulty`: Exam difficulty level (Easy, Medium, Hard)
-   `exam_proportion`: Proportion of exam answered correctly (0-1)

```{r explore-dataset3}
head(dataset3)
ggplot(dataset3, aes(x = prep_time, y = exam_proportion, color = difficulty)) +
  geom_point() +
  labs(title = "Preparation Time vs Exam Performance")
```

**Questions:** 1.
How do preparation time and exam difficulty affect performance?

```{r exercise3-solution}

```

------------------------------------------------------------------------

# Exercise 4: Hospital Daily Admissions

**Data Description:** This dataset tracks daily hospital admissions.

-   `population_thousands`: Local population in thousands (10-200)
-   `hospital_quality`: Hospital quality rating (standardized, mean=0)
-   `daily_admissions`: Count of daily admissions

```{r explore-dataset4}
head(dataset4)
ggplot(dataset4, aes(x = population_thousands, y = daily_admissions)) +
  geom_point() +
  labs(title = "Population vs Daily Hospital Admissions")
```

**Questions:** 1.
How do population size and hospital quality affect admission counts?

```{r exercise4-solution}

```

------------------------------------------------------------------------

# Exercise 5: Customer Satisfaction

**Data Description:** This dataset contains customer satisfaction ratings.

-   `service_rating`: Service quality rating (1-10)
-   `price_satisfaction`: Price satisfaction rating (1-10)
-   `satisfaction`: Overall satisfaction (1=Very Unsatisfied, 5=Very Satisfied)

```{r explore-dataset5}
head(dataset5)
table(dataset5$satisfaction)
ggplot(dataset5, aes(x = service_rating, y = satisfaction)) +
  geom_jitter(height = 0.2, alpha = 0.6) +
  labs(title = "Service Rating vs Overall Satisfaction")
```

**Questions:** 1.
How do service rating and price satisfaction predict overall satisfaction?

```{r exercise5-solution}

```

------------------------------------------------------------------------

# Exercise 6: Website Daily Clicks

**Data Description:** This dataset tracks website click counts (potentially overdispersed👀).

-   `ad_spend_hundreds`: Advertising spend in hundreds of dollars (1-50)
-   `website_age_years`: Age of website in years (0.5-5)
-   `daily_clicks`: Count of daily clicks

```{r explore-dataset6}
head(dataset6)
ggplot(dataset6, aes(x = ad_spend_hundreds, y = daily_clicks)) +
  geom_point() +
  labs(title = "Ad Spend vs Daily Clicks")

# Check for overdispersion
mean(dataset6$daily_clicks)
var(dataset6$daily_clicks)
```

**Questions:** 1.
How do advertising spend and website age affect click counts?

```{r exercise6-solution}

```

------------------------------------------------------------------------
